---
title: PrescribeIT Baseline Study
author: Dr. Neil McEvoy 
date: \today
params:
  logo: logo.png
  cover: cover.png
  iblue: 2b4894
  igray: d4dbde
documentclass: article
fontsize: 10
papersize: letter
output: 
  IReports::businessReport:
    keep_tex: TRUE
    latex_engine: xelatex
    resetStyleFiles: FALSE
header-includes: 
  - \newcommand{\logo}{`r gsub("_", "\\_", params$logo)`}
  - \newcommand{\cover}{`r gsub("_", "\\_", params$cover)`}
  - \newcommand{\iblue}{`r params$iblue`}
  - \newcommand{\igray}{`r params$igray`}
include-before:
  - \renewcommand{\contentsname}{Contents}
  - \renewcommand{\pagename}{Page}
---



```{r setup, include = FALSE}
# packages
library(dplyr)
library(knitr)
library(xtable)

# settings
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

\maketitle
\tableofcontents
\addcontentsline{toc}{section}{Table of contents}
\clearpage

\section{Background to the Study}
The baseline study reported here is the second phase of a three phase project intended to gather evidence of the benefits of PrescribeIT in prescribing and dispensing medications.

\subsection{Overall purpose}
The overall purpose of the project is to gather evidence of the benefits of PrescribeIT. 

\subsection{Summary of Phase 1 Workflow}

The first phase examined workflow at selected physician offices and dispenser outlets. The study identified patterns of flow, and exposed key processes at which changes due to PrescribeIT might contribute improvements.

\subsection{Goals of Phase 2 Baseline}

The goal of the second phase is to establish baseline indicators close to the introduction of PrescribeIT as measures against which future changes could be compared.

\subsection{Design of Phase 2 Baseline}

The phase uses indicator sets developed in light of the findings of the initial workflow phase. Each is tailored to the specifics of dispensers and prescribers repectively.

The indicators were assembled as a secure website designed for secure yet easy access.

The indicators are shown in the following tables

\section{Phase 2 Baseline Findings}

```{r results = "asis"}
tab <- xtable(head(iris, n = 20), align = "|C|C|C|C|C|C|", caption="List of sites")

addtorow <- list()
addtorow$pos <- list()
addtorow$pos[[1]] <- -1
addtorow$command <- c("\\rowcolor{igray}")

print(tab,
      include.rownames = FALSE,
      tabular.environment = "tabularx",
      width = "\\textwidth",
      comment = FALSE,
      add.to.row = addtorow)
```

\subsection{Selected sites}

The following sites were selected for participation by CHI

Prescribers:

\subsection{Prescribers}

\subsection{Dispensers}

\subsection{Salient findings}


\section{Anticipating Phase 3 Increments}

\subsection{Survey extension}

\subsection{Potential findings}

\section{Reference Materials}

